---
title: "check_ps_results"
format: html
editor: visual
---

```{r}

library(WeightIt)
```

# Transportation Density

```{r}

load('/work/hawkins_lab/vulcan/results/weight_it_transport_density-V3.RData')

```

## OptWeight - best (lots of trimming though)

```{r}
new_W_optweight = trim(W_optweight, at = 0.95, lower = FALSE, drop = FALSE)
w <- new_W_optweight$weights
threshold <- quantile(w, probs = 0.085)

w[w < threshold] <- threshold
new_W_optweight$weights <- w
summary(new_W_optweight)
```

```{r}
cobalt::bal.tab(new_W_optweight)
```
Select first model because ESS much less important than covariate balance!

```{r}
new_W_optweight1 = trim(W_optweight, at = 0.9, lower = TRUE, drop = FALSE)
summary(new_W_optweight1)
```

```{r}
cobalt::bal.tab(new_W_optweight1)
```
## Export top weights for each 5D to a csv

```{r}
df <- data.frame(dens = new_W_optweight$weights)
```

# Transportation Diversity

```{r}
load('/work/hawkins_lab/vulcan/results/weight_it_transport_diversity.RData')
```

## CBPS - best

```{r}
summary(W_cbps)
```

```{r}
cobalt::bal.tab(W_cbps)
```

## Export top weights for each 5D to a csv

```{r}
df$div = W_cbps$weights
```

# Transportation Design

```{r}
load('/work/hawkins_lab/vulcan/results/weight_it_transport_design.RData')


```

## CBPS - best

```{r}
summary(W_cbps)
```

```{r}
cobalt::bal.tab(W_cbps)
```

## Export top weights for each 5D to a csv

```{r}
df$des = W_cbps$weights
```

# Transportation Distance - log

```{r}
load('/work/hawkins_lab/vulcan/results/weight_it_transport_distance_log.RData')

```

## Entropy Balance - best

```{r}
summary(W_ebal)
```

```{r}
cobalt::bal.tab(W_ebal)
```
## Export top weights for each 5D to a csv

```{r}
df$dist = W_ebal$weights
```

# Transportation Destination

```{r}

load('/work/hawkins_lab/vulcan/results/weight_it_transport_destination-V3.RData')

```

## CBPS - best (trim more?)

```{r}
summary(W_cbps)
```

```{r}
cobalt::bal.tab(W_cbps)
```

## Export top weights for each 5D to a csv

```{r}
df$dest = W_cbps$weights

write.csv(df, file = file.path("/work/hawkins_lab/vulcan/results/tran_weights.csv"),row.names = FALSE)

```

# Electricity Density

```{r}
load('/work/hawkins_lab/vulcan/results/weight_it_electricity_density.RData')


```

## Entropy Balance - best

```{r}
new_W_ebal = trim(W_ebal, at = 0.99, lower = TRUE, drop = FALSE)
summary(new_W_ebal)
```

```{r}

cobalt::bal.tab(new_W_ebal)
```

## Export top weights for each 5D to a csv

```{r}
df <- data.frame(dens = new_W_ebal$weights)

```

# Electricity Diversity

```{r}
load('/work/hawkins_lab/vulcan/results/weight_it_electricity_diversity.RData')

```

## CBPS - best

```{r}
summary(W_cbps)
```

```{r}
cobalt::bal.tab(W_cbps)
```

## Export top weights for each 5D to a csv

```{r}
df$div = W_cbps$weights
write.csv(df, file = file.path("/work/hawkins_lab/vulcan/results/elec_weights.csv"), row.names = FALSE)
```

# Residential Density

```{r}

load('/work/hawkins_lab/vulcan/results/weight_it_residential_density.RData')


```

## CBPS - best

```{r}
summary(W_cbps)
```

```{r}
cobalt::bal.tab(W_cbps)
```

## Export top weights for each 5D to a csv

```{r}
df <- data.frame(dens = W_cbps$weights)
```

# Residential Diversity

```{r}
load('/work/hawkins_lab/vulcan/results/weight_it_residential_diversity.RData')

```

## CBPS - best

```{r}
summary(W_cbps)
```

```{r}
cobalt::bal.tab(W_cbps)
```

## Export top weights for each 5D to a csv

```{r}
df$div = W_cbps$weights
write.csv(df, file = file.path("/work/hawkins_lab/vulcan/results/res_weights.csv"), row.names = FALSE)
```
